---
title: "Summary_Data_Airbnb_Rotterdam"
author: "Nina Verschuuren, Meggy Lemmens, Amber Kalse, Nynke Voermans"
date: "2022-09-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE}
library(readr)
Airbnb_Rotterdam <- read_csv("Rotterdam.csv.gz")
```

# Explanation important variables for our research:
- price = the price of the Airbnb in Rotterdam on 7-9-22. This will be our dependent variable. This variable is measured in dollars.
- host_since = the date that the host started with their Airbnb. This is measured by a specific date.
- host_response_time = how fast the host responds. This is measured in different categories. We need to convert this.
- host_response_rate = how often the host responds. This is measured in percentages.
- host_is_superhost = says whether the host is a super host. This is a Boolean variable. We need to convert this into a dummy variable.
- host_has_profile_pic = says whether the host has a profile picture. This is a Boolean variable. We need to convert this into a dummy variable.
- host_identity_verified = indicates if the host information is verified. This is a Boolean variable. We need to convert this into a dummy variable.